A complete solution for scattering in a kind of quiver gauge theory

### 2025-04-14 Intermediate report/main.tex
New

\documentclass{beamer}
\usetheme{Madrid}
\usefonttheme{professionalfonts}
\usecolortheme{rose}
\usepackage{fontspec}
\setmainfont{Times New Roman}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{tikz}
\usepackage{svg}
\usepackage{graphics}
\usepackage{appendixnumberbeamer}
\usepackage{mathtools}
\usepackage{enumitem}
\usepackage{subcaption}
\usepackage{comment}
\usepackage[most]{tcolorbox}
\tcbset{
  thickitembox/.style={
    colback=white,
    colframe=white,
    left=2mm,
    before skip=4pt,
    after skip=4pt,
    borderline west={3pt}{0pt}{gray},  % ← 这里控制线条粗细和颜色
    enhanced,
  }
}
\setlist[itemize]{label=\textbullet}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{arrows.meta}
\setlength{\parskip}{0.3em}
\newcommand{\aket}[1]{|#1\rangle}
\newcommand{\sket}[1]{|#1]}
\newcommand{\avg}[1]{\langle #1 \rangle}
\newcommand{\mdavg}[2]{\langle #1 \rangle\!\langle #2 \rangle}
\AtBeginSection[]{
\begin{frame} 
    \frametitle{Contents}
    \tableofcontents[currentsection]
\end{frame}
}
\title[Application of BCFW]{A complete solution for scattering in a kind of quiver gauge theory}
\author{Su Yingze}
\institute{Nagoya University}
\date[4 21st 2025]{April 21st 2025}

\begin{document}
\frame{\titlepage}
\section{Why we need new method?}
\begin{frame}
    \frametitle{Why we need new method?}
    Feynman diagram is a brilliant method without doubt, but it also faces many challenges.
    \begin{itemize}
        \item How to compute high multiplicity amplitudes, like n gluons scattering.
        \item Gauge redundancies bring us many structral complications and non-physical degrees of freedom.
        \item Some symmetries are hidden, like the dual superconformal symmetry for $\mathcal{N}=4$ SYM.
        \item Is the local field theory the most basic discription for physics?
    \end{itemize}
    \includegraphics{Picture1.png}
\end{frame}
\begin{frame}
    \frametitle{From Frynman diagram to On-shell method}
    On-shell here means that all quantities we use are gauge invariant and satisfy the on-shell condition.
    Specifically, there are many ingredients under this frame
    \begin{itemize}
        \item The analytic continuation for S-matrix.
        \item The color-ordered amplitudes.
        \item The BCFW recursion relation.
        \item The spinor helicity discription for amplitudes.
    \end{itemize}
\end{frame}
\section{Preliminary}
\begin{frame}
    \frametitle{A brief introduction to BCFW}
    BCFW recursion relation is a method to compute scattering amplitude recursively, means that you can 
    compute higher point amplitudes from lower point.
    \par
 \begin{itemize}[label=\textbullet]
    \item Ruth Britto
    \item Freddy Cachazo
    \item Bo Feng
    \item Edward Witten
 \end{itemize}

@@

These vectors $r_i$ are used to define n shifted momenta
\begin{equation*}
    \hat{p}_i^\mu \equiv p_i^\mu + zr_i^\mu \qquad \text{with} z \in \mathcal{C}
\end{equation*}

@@

    Then, at a $z_I$ pole, the propagator $\hat{P}_I^2$ goes to on-shell. In that limit, the shifted amplitude
    \textcolor{red}{factorizes} into to on-shell parts (Unitarity)
    \begin{equation*}
        \hat{A}_n(z)\quad \xrightarrow{z\,\text{near}\,z_I} \quad \hat{A}_L(z_I)\frac{1}{\hat{P}_I^2}\hat{A}_R(z_I)= - \frac{z_I}{z-z_I}\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
    \end{equation*}
    This makes it easy to evaluate the residue at $z=z_I$
    \begin{equation*}
        -Res|_{z=z_I}\frac{\hat{A}_n(z)}{z}=\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)=
    \end{equation*}
\end{frame}

\begin{frame}
\frametitle{Spinor-helicity formalism}
    The critical point for Spinor-helicity formalism is that a 4-vector $p_\mu$ in $(\frac{1}{2},\frac{1}{2})$ representation can be equivalently represented by a bispinor in $(\frac{1}{2},0)\bigoplus (0,\frac{1}{2})$ representation.
    Specifically
    \begin{itemize}
        \item $\bm{\text{Massless Case}}$\\
    \begin{equation*}
        p_\mu \sigma^\mu=p_{\alpha\dot{\alpha}}=\begin{pmatrix*} 
            p^0-p^3 & -p^1+ip^2\\
            -p^1-ip^2 & p^0+p^3
        \end{pmatrix*}
    \end{equation*}
    And $p_{\alpha\dot{\alpha}}$ can be decomposed into product of two Weyl spinors
    \begin{equation*}
        p_{\alpha\dot{\alpha}}=\lambda_\alpha \tilde{\lambda}_{\dot{\alpha}}=\aket{\lambda}[\lambda|
    \end{equation*}
    Here we can find that there is a ambiguity for the definition, the momentum is invariant under the following redefinition
    \begin{equation*}
        \lambda \rightarrow t^{-1}\lambda, \qquad \tilde{\lambda}\rightarrow t\tilde{\lambda}, \qquad t\in\mathbb{C^*} 
    \end{equation*}
    same as 
    \begin{equation*}
        \aket{\lambda}\rightarrow t^-\aket{\lambda}, \qquad \sket{\lambda}\rightarrow t\sket{\lambda}
    \end{equation*}
    \end{itemize}
\end{frame}

@@

\begin{frame}
    Similarly, we can also obtain
    \begin{equation*}
        2h_2=-x_{12}-x_{23},\qquad 2h_3=-x_{13}-x_{23}.
    \end{equation*}
    Then all index can be solved from this system of equations, so that
    \begin{equation*}
        A_3^{h_1h_2h_3}=c\avg{12}^{h_3-h_1-h_2}\avg{31}^{h_2-h_1-h_3}\avg{23}^{h_1-h_2-h_3}\quad h_1+h_2+h_3<0.
    \end{equation*}
    Also for square brackets case, we can obtain
    \begin{equation*}
        A_3^{h_1h_2h_3}=c^{'}[12]^{h_1+h_2-h_3}[23]^{h_2+h_3-h_1}[31]^{h_3+h_1-h_2}\quad h_1+h_2+h_3>0.
    \end{equation*}
    \textbf{Example}: 3-gluon amplitude\\
    \begin{equation*}
        A_3(g_1^-,g_2^-,g_3^+)=g\frac{\avg{12}^3}{\avg{23}\!\avg{31}}
    \end{equation*}
\end{frame}
\section{Introduction of quiver gauge theory}
\begin{frame}
    \frametitle{Introduction of Quiver of Moose gauge theory}
    \begin{itemize}
        \item Quiver: A container for carring arrows
        \item Moose: A kind of deer with large horns 
    \end{itemize}

>>>>

\documentclass{beamer}
\usetheme{Madrid}
\usefonttheme{professionalfonts}
\usecolortheme{rose}
\usepackage{fontspec}
\setmainfont{Times New Roman}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{svg}
\usepackage{graphics}
\usepackage{appendixnumberbeamer}
\usepackage{mathtools}
\usepackage{enumitem}
\usepackage{subcaption}
\usepackage{comment}
\usepackage[most]{tcolorbox}
\tcbset{
  thickitembox/.style={
    colback=white,
    colframe=white,
    left=2mm,
    before skip=4pt,
    after skip=4pt,
    borderline west={3pt}{0pt}{gray},  % ← 这里控制线条粗细和颜色
    enhanced,
  }
}
\setlist[itemize]{label=\textbullet}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{arrows.meta}
\setlength{\parskip}{0.3em}
\newcommand{\aket}[1]{|#1\rangle}
\newcommand{\sket}[1]{|#1]}
\newcommand{\avg}[1]{\langle #1 \rangle}
\newcommand{\mdavg}[2]{\langle #1 \rangle\!\langle #2 \rangle}
\AtBeginSection[]{
\begin{frame} 
    \frametitle{Contents}
    \tableofcontents[currentsection]
\end{frame}
}
\title[Application of BCFW]{A complete solution for scattering in a kind of quiver gauge theory}
\author{Su Yingze}
\institute{Nagoya University}
\date[4 21st 2025]{April 21st 2025}

\begin{document}
\frame{\titlepage}
\section{Why we need new method?}
\begin{frame}
    \frametitle{Why we need new method?}
    Feynman diagram is a brilliant method without doubt, but it also faces many challenges.
    \begin{itemize}
        \item How to compute high multiplicity amplitudes, like n gluons scattering.
        \item Gauge redundancies bring us many structral complications and non-physical degrees of freedom.
        \item Some symmetries are hidden, like the dual superconformal symmetry for $\mathcal{N}=4$ SYM.
        \item Is the local field theory the most basic discription for physics?
    \end{itemize}
\end{frame}
\begin{frame}
    \frametitle{From Frynman diagram to On-shell method}
    On-shell here means that all quantities we use are gauge invariant and satisfy the on-shell condition.
    Specifically, there are many ingredients under this frame
    \begin{itemize}
        \item The analytic continuation for S-matrix.
        \item The color-ordered amplitudes.
        \item The BCFW recursion relation.
        \item The spinor helicity discription for amplitudes.
    \end{itemize}
\end{frame}
\section{Preliminary}
\begin{frame}
    \frametitle{A brief introduction to BCFW}
    BCFW recursion relation is a method to compute scattering amplitude recursively, means that you can 
    compute higher point amplitudes from lower point.
    \par
 \begin{itemize}[label=\textbullet]
    \item Ruth Britto
    \item Freddy Cachazo
    \item Bo Feng
    \item Edward Witten
 \end{itemize}

@@

These vectors $r_i$ are used to define n shifted momenta
\begin{equation*}
    \hat{p}_i^\mu \equiv p_i^\mu + zr_i^\mu \qquad \text{with} z \in \mathcal{C}
\end{equation*}
Then, $\hat{P}_I^2$ is \textcolor{red}{linear} in z:
\begin{equation*}
    \hat{P}_I^2=\left(\sum_{i\in I} \hat{p}_i \right) ^2 = P_I^2 +2zP_I\cdot R_I \quad \text{with} \quad R_I=\sum_{i\in I} r_i ,
\end{equation*}

@@

    Then, at a $z_I$ pole, the propagator $\hat{P}_I^2$ goes to on-shell. In that limit, the shifted amplitude
    \textcolor{red}{factorizes} into to on-shell parts (Unitarity)
    \begin{equation*}
        \hat{A}_n(z)\quad \xrightarrow{z\,\text{near}\,z_I} \quad \hat{A}_L(z_I)\frac{1}{\hat{P}_I^2}\hat{A}_R(z_I)= - \frac{z_I}{z-z_I}\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)
    \end{equation*}
    This makes it easy to evaluate the residue at $z=z_I$
    \begin{equation*}
        -Res|_{z=z_I}\frac{\hat{A}_n(z)}{z}=\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)=\raisebox{-1em}{\includegraphics[height=3em]{recrel1.pdf}}   
    \end{equation*}
\end{frame}

\begin{frame}
    \frametitle{Large z behavior}
    In the BCFW formula, the boundary term $B_n$ affects a lot
    \begin{equation*}
        A_n=-\sum_{z_I}Res|_{z=z_I}\frac{\hat{A}_n(z)}{z}+B_n,
    \end{equation*}
    In most applications. one assumes or much better, proves $B_n=0$. This is often justified by declaring a stronger condition
    \begin{equation*}
        \textcolor{red}{\hat{A}_n(z)\rightarrow 0 \quad \text{for} \quad z\rightarrow \infty} 
    \end{equation*}
    Here I show the large z behavior for gluon scattering 
    \begin{center}
        \begin{tabular}{lrc}
            \toprule
            $[i\, \textbackslash \, j\rangle $ & $+$ & $-$ \\
            \midrule
            $+$ & $1/z$ & $z^3$ \\
            $-$ & $1/z$ & $1/z$ \\
            \bottomrule
          \end{tabular}
    \end{center}

\end{frame}

\begin{frame}
\frametitle{Spinor-helicity formalism}
    The critical point for Spinor-helicity formalism is that a 4-vector $p_\mu$ in $(\frac{1}{2},\frac{1}{2})$ representation can be equivalently represented by a bispinor in $(\frac{1}{2},0)\bigoplus (0,\frac{1}{2})$ representation.
    Specifically
    \begin{itemize}
        \item $\bm{\text{Massless Case}}$\\
    \begin{equation*}
        p_\mu \sigma^\mu=p_{\alpha\dot{\alpha}}=\begin{pmatrix*} 
            p^0-p^3 & -p^1+ip^2\\
            -p^1-ip^2 & p^0+p^3
        \end{pmatrix*}
    \end{equation*}
    And $p_{\alpha\dot{\alpha}}$ can be decomposed into product of two Weyl spinors
    \begin{equation*}
        p_{\alpha\dot{\alpha}}=\lambda_\alpha \tilde{\lambda}_{\dot{\alpha}}=\aket{\lambda}[\lambda|
    \end{equation*}
    Here we can find that there is a ambiguity for the definition, the momentum is invariant under the following redefinition
    \begin{equation*}
        \lambda \rightarrow t^{-1}\lambda, \qquad \tilde{\lambda}\rightarrow t\tilde{\lambda}, \qquad t\in\mathbb{C^*} 
    \end{equation*}
    same as 
    \begin{equation*}
        \aket{\lambda}\rightarrow t^{-1}\aket{\lambda}, \qquad \sket{\lambda}\rightarrow t\sket{\lambda}
    \end{equation*}
    \end{itemize}
\end{frame}

@@

\begin{frame}
    Similarly, we can also obtain
    \begin{equation*}
        2h_2=-x_{12}-x_{23},\qquad 2h_3=-x_{13}-x_{23}.
    \end{equation*}
    Then all index can be solved from this system of equations, so that
    \begin{equation*}
        A_3^{h_1h_2h_3}=c\avg{12}^{h_3-h_1-h_2}\avg{31}^{h_2-h_1-h_3}\avg{23}^{h_1-h_2-h_3}\quad h_1+h_2+h_3<0.
    \end{equation*}
    Also for square brackets case, we can obtain
    \begin{equation*}
        A_3^{h_1h_2h_3}=c^{'}[12]^{h_1+h_2-h_3}[23]^{h_2+h_3-h_1}[31]^{h_3+h_1-h_2}\quad h_1+h_2+h_3>0.
    \end{equation*}
    \textbf{Example}: 3-gluon amplitude\\
    \begin{equation*}
        A_3(g_1^-,g_2^-,g_3^+)=g\frac{\avg{12}^3}{\avg{23}\!\avg{31}}
    \end{equation*}
\end{frame}
\section{Introduction of quiver gauge theory}
\begin{frame}
    \frametitle{Introduction of Quiver or Moose gauge theory}
    \begin{itemize}
        \item Quiver: A container for carring arrows
        \item Moose: A kind of deer with large horns 
    \end{itemize}
